\textbf{COMP0078 Assignment 2}

### 2022-12-14 submission.tex
spelling

        A reasonable explanation for the kernel approach's superior performance follows from the observation that seminorm interpolation propagates local information to pass labels through the graph, whereas the kernel method utilises global graph connectivity
        properties of each point to a set of labels to make predictions.
        This means that in the seminorm method, only datapoints close to labelled data receive information from the labels themselves, and accuracy is likely reduced for datapoints far from the labels as label information is passed indirectly through the graph.
        Further if a point is close the the boundary of a cluster, it may be be misclassified due to its proximity to a single label from the other cluster. 
        In contrast, the kernel interpolation method takes global information from all the labelled datapoints and weights them according to their connectedness through the graph to a given vertex to determine a predicted label.
        A vertex will only be given a label if it is more strongly connected to all labelled points that have this label. This use of global information helps to resolve the case in which a vertex lies on the boundary of the two clusters as the model draws
        conclusions directly from its connectedness to labelled points rather than recieving information from similarly ambiguous boundary points. However, we should note that this superior performance is an artifact of the dataset,
        and that it separates well into one cluster per datapoint: this implies that if a vertex is more strongly connected to points with label +1, then it is most likely given this label in reality.
    \item[4.]
        We may postulate that the seminorm interpolation method may outperform the kernel method on datasets where global information is more ambiguous than local information: for instance, consider a graph where there are more than 2 clusters, each with coherent binary labelling, but perhaps where 2 clusters of the same label are separated by a cluster of different labelling. In this scenario, the seminorm method would label the data in 3 clusters, by only considering local edgewise label changes, but the kernel method may have difficulty correctly identifying the label for some vertices as it may be less connected to points of the same label in ground truth, than to points of a different label in the neighbouring cluster. 
\end{itemize}

>>>>

        A reasonable explanation for the kernel approach's superior performance follows from the observation that seminorm interpolation propagates local information to pass labels through the graph, whereas the kernel method utilises global graph connectivity
        properties of each point to a set of labels to make predictions.
        This means that in the seminorm method, only datapoints close to labelled data receive information from the labels themselves, and accuracy is likely reduced for datapoints far from the labels as label information is passed indirectly through the graph.
        Further if a point is close the boundary of a cluster, it may be be misclassified due to its proximity to a single label from the other cluster.
        In contrast, the kernel interpolation method takes global information from all the labelled datapoints and weights them according to their connectedness through the graph to a given vertex to determine a predicted label.
        A vertex will only be given a label if it is more strongly connected to all labelled points that have this label. This use of global information helps to resolve the case in which a vertex lies on the boundary of the two clusters as the model draws
        conclusions directly from its connectedness to labelled points rather than receiving information from similarly ambiguous boundary points. However, we should note that this superior performance is an artifact of the dataset,
        and that it separates well into one cluster per datapoint: this implies that if a vertex is more strongly connected to points with label +1, then it is most likely given this label in reality.
    \item[4.]
        We may postulate that the seminorm interpolation method may outperform the kernel method on datasets where global information is more ambiguous than local information: for instance, consider a graph where there are more than 2 clusters, each with coherent binary labelling, but perhaps where 2 clusters of the same label are separated by a cluster of different labelling. In this scenario, the seminorm method would label the data in 3 clusters, by only considering local edgewise label changes, but the kernel method may have difficulty correctly identifying the label for some vertices as it may be less connected to points of the same label in ground truth, than to points of a different label in the neighbouring cluster. 
\end{itemize}
